\documentclass[]{article}

%opening
\title{Agenda for the Dinner}
\author{}

\begin{document}

\maketitle

\begin{abstract}
Perhaps as in Babette's Feast, we hope to use a dinner gathering to promote of sense of inclusiveness and comfort, both among each other, and also with computing, as a career, possibly of interest to the whole family, at least approved of by family members, for family members.
\end{abstract}

\section{Welcome and Introductions by Professor Sixia Chen}
Introduce Lillarnd ``Jay'' Lewis, CCSU undergraduate, (see )http://fox61.com/2014/12/20/the-stan-simpson-show-chef-jay-lewis-on-cooking-and-being-a-gentleman/)
will cook this meal for us.

\section{Meal}

\section{Address on CCSU as a welcoming, inclusive, environment}
Maybe the marketing department will provide someone.

\section{After dinner entertainment}
Computer Science Club at CCSU, robotics show

Today, 10:47 AM
Smith, Therese M. (Computer Science) 
Hello Therese, 

Sounds like a great opportunity. I'll speak to the rest of the CS Club officers about it and gauge their opinions.

It sounds interesting, but I'll need to figure out if the others believe so too, so I'll reply soon with what we decide.

Thanks!

Dan Kostecki

From: Smith, Therese M. (Computer Science)
Sent: Thursday, October 12, 2017 9:49:18 AM
To: Kostecki, Daniel (Student)
Subject: kids and robots event

Hi Dan,
Your name was given by Professor Williams.
Professor Chen and I are working on a grant application, and included is a dinner, hosted by a chef who is a student at CCSU. The theme is (because the granting organization wants it that way) using a family dinner to help influence family attitudes about children becoming interested in computing. So, one part is to have after-dinner entertainment involving robots doing something; maybe that could be racing, building, competing. Would you and your club be interested in this? 
I have a contact from a high school robotics club, too; I haven't contacted them yet. So, maybe we could have a competition if you and they like the idea. Please let me know.
Cheers,
Therese

\section{Book signing}
The Now You're Cooking with Python cookbook will be given away. This cookbook will have recipes for food, and also for getting started with code, such as with Scratch (and Python).
\end{document}
